### 2025-05-05 research-methods.qmd
20250505 - addition and typos

Test–retest reliability evaluates the consistency of scores across time.
For a construct that is expected to be stable across time (e.g., hand size in adults), we would expect our measurements to be consistent across time.
The consistency of scores across time can be examined in terms of relative or absolute test–retest reliability.
Relative test–retest reliability—i.e., the consistency of individual differences across time—is commonly evaluated using the coefficient of stability (i.e., the Pearson correlation coefficent).
Absolute test–retest reliability—i.e., the absolute consistency of people's scores across time—is commonly evaluated using the coefficient of repeatability.

@@

Parallel-forms reliability evaluates the consistency of scores across different but equivalent forms of a measure.
If we develop two equivalent versions of the Wonderlic Contemporary Cognitive Ability Test (Form A and Form B) so that players sitting next to each other do not receive the same items, we would expect a player's score on Form A would be similar to their score on Form B.
Parallel-forms reliability is is commonly evaluated using the coefficient of equivalence (i.e., the Pearson correlation coefficent).

>>>>

Test–retest reliability evaluates the consistency of scores across time.
For a construct that is expected to be stable across time (e.g., hand size in adults), we would expect our measurements to be consistent across time.
The consistency of scores across time can be examined in terms of relative or absolute test–retest reliability.
Relative test–retest reliability—i.e., the consistency of individual differences across time—is commonly evaluated using the coefficient of stability (i.e., the Pearson correlation coefficient).
Absolute test–retest reliability—i.e., the absolute consistency of people's scores across time—is commonly evaluated using the coefficient of repeatability and the coefficient of agreement (i.e., intraclass correlation coefficient).

@@

Parallel-forms reliability evaluates the consistency of scores across different but equivalent forms of a measure.
If we develop two equivalent versions of the Wonderlic Contemporary Cognitive Ability Test (Form A and Form B) so that players sitting next to each other do not receive the same items, we would expect a player's score on Form A would be similar to their score on Form B.
Parallel-forms reliability is is commonly evaluated using the coefficient of equivalence (i.e., the Pearson correlation coefficient).
